`flippant` -- An `R` package for the automated  analysis of dithionite scramblase

### 2015-09-19 inst/manuscript/manuscript.rmd
Put in first analysis step;

```{r, echo = FALSE}
library(magrittr, quietly = TRUE)
library(stringi, quietly = TRUE)
flippant_dependencies <- packageDescription("flippant",fields=c("Depends","Imports")) %>%
  unlist(use.names = FALSE) %>%
  stri_split(regex = ",", omit_empty = TRUE) %>%
  unlist(use.names = FALSE) %>%
  stri_replace_all(replacement = "", regex = "\\s*\\(.*\\)\\s*", omit_empty = TRUE) %>%
  stri_replace_all(replacement = "", regex = "\\s*", omit_empty = TRUE) %>%
  tail(n=length(.) - 1) %>%
  sort() %>%
  ( function(x){
    paste0(
      c(
        "`",
        paste0(head(x, n = length(x) - 1), collapse = "`, `"),
        "` and `",
        tail(x, n = 1),
        "`"),
      collapse = "")} )
library(flippant, quietly = TRUE)
```

@@

`flippant`s capabilities are demonstrated here by reanalyzing the data underlying 
Figure 5b in @ploier_perturbed_submitted.

>>>>

```{r, echo = FALSE}
library(flippant, quietly = TRUE)
library(grid, quietly = TRUE)
library(magrittr, quietly = TRUE)
library(multipanelfigure, quietly = TRUE)
library(stringi, quietly = TRUE)
flippant_dependencies <- packageDescription("flippant",fields=c("Depends","Imports")) %>%
  unlist(use.names = FALSE) %>%
  stri_split(regex = ",", omit_empty = TRUE) %>%
  unlist(use.names = FALSE) %>%
  stri_replace_all(replacement = "", regex = "\\s*\\(.*\\)\\s*", omit_empty = TRUE) %>%
  stri_replace_all(replacement = "", regex = "\\s*", omit_empty = TRUE) %>%
  tail(n=length(.) - 1) %>%
  sort() %>%
  ( function(x){
    paste0(
      c(
        "`",
        paste0(head(x, n = length(x) - 1), collapse = "`, `"),
        "` and `",
        tail(x, n = 1),
        "`"),
      collapse = "")} )

tmpDir <- tempdir()
file.path("extdata", "PloierEtAl_Data.zip") %>%
  system.file(
    package = "flippant",
    mustWork = TRUE) %>%
  unzip(
    overwrite = TRUE,
    exdir = tmpDir)

figure1 <- multipanelfigure(
  width = 17.22, 
  height = 18, 
  units = "cm", 
  columns = 2, 
  rows = 2)

knitr::opts_chunk$set(fig.width=6.78, fig.height=6.78, warning=FALSE, message=FALSE)
```

@@

`flippant`s capabilities are demonstrated here by reanalyzing the data underlying 
Figure 5b in @ploier_perturbed_submitted. The following work flow in a first 
step plots spectral traces for all points of the data set (Figure 1A). Note that
alorithmic alignment to the time of dithionite addition is employed (default) as
well as custom trimming of the time axis to account for divergent acquisition 
times between experiments.
<!-- Fix F220CEx1_E.txt to F220CEx1_D.txt -->
```{r, eval = FALSE}
# Plot spectral traces (Figure 1A)
scramblaseAssayTraces("inputTable.txt", timeMax = 350)
```
```{r, echo = FALSE, warning=FALSE, message=FALSE, fig.cap = "**`flippant`-based reanalysis of data in Figure 5b from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblaseAssayTraces`."}
setwd(tmpDir)
figure1 <- addpanel(
  figure = figure1,
  topPanel = 1, 
  leftPanel = 1, 
  rightPanel = 2, 
  panel = scramblaseAssayTraces("inputTable.txt", timeMax = 350)
)
grid.draw(figure1)
```
